Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/barriers.tex
merge barriers paragraph into one paragraph
Minor edit.

\OMIT{
\gaedit{Even though welfare is highest in the temporary monopoly case there are other reasons one may worry about a single firm having a substantial market share. In this section we explore what drives the substantial market share of the temporary monopolist and discuss how this relates to thinking about data as a barrier to entry.}\swcomment{maybe articulate the ``other'' reasons?}
}
\gaedit{In this section we explore what factors drive the large market share for the incumbent in the temporary monopoly.}

Under temporary monopoly, the incumbent can explore without incurring immediate reputational costs, and build up a high reputation before the entrant appears. Thus, the early entry gives the incumbent both a \textit{data} advantage and a \textit{reputational} advantage over the entrant. \gaedit{First, our findings provide a quantitative insight into the role of the classic ``first mover advantage" phenomenon in the digital economy. Second, our findings provide a viewpoint in terms of thinking about the role that data can play as a competitive advantage.}

@@

\gaedit{Our findings imply two aspects of how and when data can serve as a barrier to entry.

The first is that small asymmetries in data between firms can amplify into large effects through the same mechanism as the death spiral effect discussed in the previous section.

The second is that data can serve as a larger barrier to entry when exploration is reputationally costly. This is due to the fact that the incumbent can explore actions in the incumbency period without immediate reputational consequences, whereas in order for the entrant to acquire the same data it needs to incur the immediate reputational consequences. As a result, when the incumbent does exploration in the incumbency period the value of the data accumulated is higher and it is harder for an entrant to compete in the market.
}

>>>>

\OMIT{
\gaedit{Even though welfare is highest in the temporary monopoly case there are other reasons one may worry about a single firm having a substantial market share. In this section we explore what drives the substantial market share of the temporary monopolist and discuss how this relates to thinking about data as a barrier to entry.}\swcomment{maybe articulate the ``other'' reasons?}
}

\asdelete{We explore what factors drive the large market share for the incumbent in the temporary monopoly model.}

Under temporary monopoly, the incumbent can explore without incurring immediate reputational costs, and build up a high reputation before the entrant appears. Thus, the early entry gives the incumbent both a \textit{data} advantage and a \textit{reputational} advantage over the entrant. \asedit{We explore which of the two factors is more significant.}  \gaedit{First, our findings provide a quantitative insight into the role of the classic ``first mover advantage" phenomenon in the digital economy. Second, our findings provide a viewpoint in terms of thinking about the role that data can play as a competitive advantage.}

@@

\gaedit{Our findings imply two aspects of how and when data can serve as a barrier to entry. The first is that small asymmetries in data between firms can amplify into large effects through the same mechanism as the death spiral effect discussed in the previous section. The second is that data can serve as a larger barrier to entry when exploration is reputationally costly. This is due to the fact that the incumbent can explore actions in the incumbency period without immediate reputational consequences, whereas in order for the entrant to acquire the same data it needs to incur the immediate reputational consequences. As a result, when the incumbent does exploration in the incumbency period the value of the data accumulated is higher and it is harder for an entrant to compete in the market.
}
